---
title: "Data Analysis"
author: "Phuong"
date: "4/7/2019"
output: 
 md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# __Data Analytics and Its Application__

A broad array of companies ranging from the largest global banks to regional transport firms are using data analytics to solve diverse sets of problems These diverse applications have one commonality: using data and statistics as the basis for decision making.

## __Data Analytics__
Analytics is defined as the process of developing the actionable insights through the application of statistical model and analysis from the data. Applying data analytics
for decision making is a systematic process.

## __Data Collection__
The first step in the process is data collection. Data relevant to the applicant is collected. The quality, quantity, validity, and nature of data directly impact the analytical outcome.

## __Data Preparation__
Usually raw data is not in a format that can be directly used to perform data analysis. In very simple terms, most platforms require data to be in a matrix form with the variables being in different columns and rows representing various observations.

## __Data Analysis__
Once data is converted into a structured format, the next stage is to perform data analysis. At this stage underlying trends in the data are identified. This step can include fitting a linear or nonlinear regression model, performing principal component analysis or cluster analysis, identifying if data is normally distributed or not.

## __Model Building__
Put the data to work and build a model that will help with the given application or help solve a business problem. A vast number of statistical models are available that can be used, and new models are being developed every day.

Results obtained from the models are validated to ensure accuracy and model robustness. This can be done two ways; the first is by splitting the original data set into training and validation data sets. In this approach, part of the data is used for model building and the remaining part is used for validation. The other approach is to validate data against real-time data once the model is deployed.

Once the model is developed it is deployed in a real-time setting for a given application.

## __Types of Analytics__

### Descriptive Analytics

### Predictive Analytics

### Prescriptive Analytics

## __Understanding Data and Its Types__

### Qualitative data

### Quantitative data

## __Big Data Analytics__

### Big Data Analytics Challenges

### Big Data Analytics Tools

#### R

#### SAS (Statistical Analysis System) 

#### IBM SPSS Statistics and SPSS Modeler: Data Mining and Text Analytics Software

#### Python

#### Rapid Miner


## __Examples__
```{r cars}
summary(cars)
```

## __Ploting and ggplot2__

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
